\documentclass[helvetica,english,logo,notitle,totpages,utf8]{europecv2013}
\usepackage{graphicx}
\usepackage[a4paper,top=1.2cm,left=1.2cm,right=1.2cm,bottom=2.5cm]{geometry}
\usepackage[english]{babel}
\usepackage[T1]{fontenc}
\usepackage{natbib}
\usepackage{bibentry}

\ecvname{Betty Smith}
\ecvaddress{32 Reading rd, Birmingham B26 3QJ United Kingdom}
\ecvtelephone[+44 2012345679]{+44 7123456789}
\ecvemail{smith@kotmail.com}
\ecvlinkedin{\href{http://it.linkedin.com/in/betty.smith}{linkedin.com/in/betty.smith}}
\ecvgender{Female}
\ecvdateofbirth{01 March 1975}

\ecvfootnote{© European Union, 2002-2013 | http://europass.cedefop.europa.eu}
%\ecvbeforepicture{\raggedleft}
%\ecvpicture[width=2.5cm]{fototessera}
%\ecvafterpicture{\ecvspace{-37mm}}

\begin{document}
\selectlanguage{english}

\begin{europecv}
\ecvpersonalinfo[10pt]

\ecvposition{Job applied for}{European project manager}

\ecvsection{Work experience}

\ecvworkexperience{August 2002 -- Present}{Independent consultant}{British Council}{123, Bd Ney, 75023 Paris (France)}{Evaluation of European Commission youth training support measures for youth national agencies and young people}

\ecvworkexperience{March 2002 -- July 2002}{Internship}{European Commission, Youth Unit, DG Education and Culture}{
- evaluating youth training programmes for SALTO UK and the partnership between the Council of Europe and European Commission\par
- organizing and running a 2 day workshop on non-formal education for Action 5 large scale projects focusing on quality, assessment and recognition\par
- contributing to the steering sroup on training and developing action plans on training forthe next 3 years. Working on the Users Guide for training and the support measures}

\ecvworkexperience{October 2001 – February 2002}{Researcher / Independent Consultant}{Council of Europe, Budapest (Hungary)}{}{Working in a research team carrying out in-depth qualitative evaluation of the 2 year Advanced Training of Trainers in Europe using participant observations, in-depth interviews and focus groups.\par
Work carried out in training courses in Strasbourg, Slovenia and Budapest.}

\ecvsection{Education and training}

\ecveducation{1997 -- 2001}{PhD - Thesis Title: `Young People in the Construction of the Virtual University', Empirical research on e-learning}{Brunel University, London United Kingdom}{}{}

\ecveducation{1993 -- 1997}{Bachelor of Science in Sociology and Psychology}{Brunel University, London United Kingdom}{
- sociology of risk\par
- sociology of scientific knowledge / information society\par
- anthropology\par
E-learning and Psychology\par
- research methods}{}

\ecvsection{Personal skills}

\ecvmothertongue[20pt]{English}
\ecvlanguageheader
\ecvlanguage{French}{C1}{C2}{B2}{C1}{C2}
\ecvlastlanguage{German}{A2}{A2}{A2}{A2}{A2}
\ecvlanguagefooter[10pt]

\ecvitem[10pt]{Communication skills}{
- team work: I have worked in various types of teams from research teams to national league hockey. For 2 years I coached my university hockey team\par
- mediating skills: I work on the borders between young people, youth trainers, youth policy and researchers, for example running a 3 day workshop at CoE Symposium `Youth Actor of Social Change', and my continued work on youth training programmes\par
- intercultural skills: I am experienced at working in a European dimension such as being a rapporteur at the CoE Budapest `youth against violence seminar' and working with refugees.}

\ecvitem[10pt]{Organisational / managerial skills}{
- whilst working for a Brussels based refugee NGO `Convivial' I organized a `Civil Dialogue between refugees and civil servants at the European Commission 20th June 2002\par
- during my PhD I organised a seminar series on research methods}

\ecvitem[10pt]{Computer skills}{Creating pieces of Art and visiting Modern Art galleries. Enjoy all sports particularly hockey, football and running. Love to travel and experience different cultures.}

\ecvitem[10pt]{Other skills}{Creating pieces of Art and visiting Modern Art galleries. Enjoy all sports particularly hockey, football and running. Love to travel and experience different cultures.}

\ecvitem[10pt]{Driving licence}{A, B}


\bibliographystyle{plain}
\nobibliography{publications-en}

\ecvsection{ADDITIONAL INFORMATION}

\ecvitem{Publications}{\bibentry{pub1}}

\end{europecv}
\end{document} 
